The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-01-17 SC-challenge.tex
Comment about software citing other software
Typo

Key challenges and research directions include the need to:
\begin{itemize}
\item identify necessary metadata associated with software for citation, 
\item standardize proper formats for citing software in publications,
\item establish mechanisms for software to cite other software (i.e., dependencies),
\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
\item determine standard practices for peer review of software, and
\item increase cultural acceptance of the concept of software as a digital product.
\end{itemize}

@@

However, research and development efforts are needed to solve the remaining challenges.
These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not publicly preserved?
How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since in order for software citations to carry weight akin to publications for academic credit and reputation, they require such indexing to create a similar citation network?
How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors?
Should such a citation be ``weighted'' higher than others?
The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementary data~\cite{Katz:2015aa}.

>>>>

Key challenges and research directions include the need to:
\begin{itemize}
\item identify necessary metadata associated with software for citation, 
\item standardize proper formats for citing software in publications,
\item establish mechanisms for software to cite other software (i.e., dependencies),
% I feel like we should point out that this problem has been solved by multiple communities already (Node.js/NPM, Ruby/Gemfile)
\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem,
\item determine standard practices for peer review of software, and
\item increase cultural acceptance of the concept of software as a digital product.
\end{itemize}

@@

However, research and development efforts are needed to solve the remaining challenges.
These questions include: how can we cite closed-source\slash commercial software---can the above information be provided, even if the the software itself is not publicly preserved?
How will index services (e.g., Web of Science, Scopus, Google Scholar) fully index software, since in order for software citations to carry weight akin to publications for academic credit and reputation, they require such indexing to create a similar citation network?
How can publications indicate direct use of software for research in citations, where results would not be possible without efforts of software authors?
Should such a citation be ``weighted'' higher than others?
The \citeN{AAS:2016} suggests a new ``Software'' section below the acknowledgements; other approaches include machine-readable supplementany data~\cite{Katz:2015aa}.
